---
title: "Kelly-Criterion"
author: "englianhu"
website: <https://jp.linkedin.com/in/englianhu>
date: "Thursday, December 25, 2014"
output: html_document
---

I tried to scrap the odds price from 7M and NowGoal website, and apply Kelly-Criterion Model, from the simulatioin we can know that the EM model is profitable. However real-time trading platform is the future project which need to start soon... <https://github.com/englianhu/Kelly-Criterion>.

Load and manipulate the dataset.
```{r}
require('turner', quietly=TRUE)

load('./data/dataset.RData')
COModds <- subset(COM_7M1213$AH, names(COM_7M1213$AH) %in% eng1213$MatchID_7M)

# initial odds price
ini.odds <- lapply(COModds, function(x) na.omit(x)[1,-1])
ini.odds <- lapply(ini.odds, function(x){ df_to_blocks(x,blocks=c(rep(3,ncol(x)/3)),byrow=FALSE)})
ini.odds2 <- lapply(seq(ini.odds), function(i) {
  lapply(seq(ini.odds[[i]]),function(j) {
    COM=substr(names(ini.odds[[i]][[j]]),1,nchar(names(ini.odds[[i]][[j]]))-3)[1]
    names(ini.odds[[i]][[j]])=c('AH','HM','AW')
    data.frame(MatchID=names(ini.odds)[[i]], COM, ini.odds[[i]][[j]])}) })
iniOdds <- Reduce(function(x, y) merge(x, y, all = T), unlist(ini.odds2, recursive=F), accumulate = F)
iniOdds <- iniOdds[iniOdds$MatchID %in% EM_7M1213$FT$FTAH$MatchID,]
iniOdds$Spreads <- iniOdds$HM + iniOdds$AW
rm(ini.odds, ini.odds2)
```

Manipulate and reshape the dataset
```{r}
library('reshape2')

# EM_7M1213$FT$FTAH[,1:5]
# filter the soccer matches which the teams has selected to calculated
eng1213b <- subset(eng1213, MatchID_7M %in% EM_7M1213$FT$FTAH$MatchID)
nrow(EM_7M1213$FT$FTAH)

# filter the initial odds data from 7M by MatchID
dat <- EM_7M1213$FT$FTAH[EM_7M1213$FT$FTAH$MatchID %in% iniOdds$MatchID,]
# nrow(EM_7M1213$FT$FTAH[EM_7M1213$FT$FTAH$MatchID %in% iniOdds$MatchID,])
ah <- ifelse(nchar(abs(iniOdds$AH*100))<3, paste0('0',abs(iniOdds$AH*100)),iniOdds$AH*100)
ah <- ifelse(substr(ah,1,1)=='-', paste0('HN',ah), paste0('HP',ah))
ah <- gsub('-', '', ah); iniOdds$AHCode <- gsub('HP00', 'H000', ah); rm(ah)
iniOdds$AHCode <- as.factor(iniOdds$AHCode)
iniHM <- iniOdds[c("MatchID","COM","AH","HM","AHCode","Spreads")]; iniHM$AH <- -iniHM$AH
iniAW <- iniOdds[c("MatchID","COM","AH","AW","AHCode","Spreads")]
iniAW$AHCode <- gsub('HN','AP',iniAW$AHCode); iniAW$AHCode <- gsub('HP','AN',iniAW$AHCode)
iniAW$AHCode <- gsub('H000','A000',iniAW$AHCode)
iniOdds <- merge(iniHM, iniAW, all=T)
iniOdds$AH <- ifelse(substr(iniOdds$AHCode,2,2)=='N', -abs(iniOdds$AH), abs(iniOdds$AH))
iniOdds$COMOdds <- ifelse(is.na(iniOdds$HM) & !is.na(iniOdds$AW), iniOdds$AW,
                       ifelse(!is.na(iniOdds$HM) & is.na(iniOdds$AW), iniOdds$HM, NA))
iniOdds <- iniOdds[c('MatchID','COM','AH','AHCode','COMOdds','Spreads')]
iniOdds$RProb <- iniOdds$COMOdds * 2/iniOdds$Spreads
rm(iniHM, iniAW)
```

Merge the dataset
```{r}
# Filter the MatchID of EM_7M and iniOdds
EMOdds <- melt(EM_7M1213$FT$FTAH,id=c('MatchID','Round','KODate','Home',
                                      'Away','FTHG','FTAG','HTHG','HTAG'),
               variable.name='AHCode', value.name='EMprob')
length(unique(EMOdds$MatchID))
length(unique(iniOdds$MatchID))

# merge iniOdds and EMOdds
mbase <- merge(iniOdds, EMOdds, by=c("MatchID","AHCode"))
mbase$AH <- ifelse(substr(mbase$AHCode,2,2)=='N', -abs(mbase$AH), abs(mbase$AH))
```

AH Calculator and Kelly-Betting
```{r}
# -----------------------------------------------------------------------------
# Kelly criterion
# Advantages = (prob of win * decimal odds) + (prob of lose * -1)
# Optimal Kelly wager % = Advantages / decimal odds
mbase$Adv <- (mbase$EMprob * mbase$COMOdds) + ((1-mbase$EMprob) * -1)
mbase$Staking <- mbase$Adv / mbase$COMOdds
mbase$Staking <- ifelse(mbase$Staking < 0, 0, mbase$Staking)

# Measure the advantage (pure odds without overround/margin)
mbase$Adv2 <- (mbase$EMprob * mbase$RProb) + ((1-mbase$EMprob) * -1)
mbase$Staking2 <- mbase$Adv2 / mbase$COMOdds
mbase$Staking2 <- ifelse(mbase$Staking2 < 0, 0, mbase$Staking2)

# AH & OU Calculator
mbase$Output <- 0
for(i in seq(mbase$AH)){
  if(substr(mbase$AHCode[i], 1, 1)=='H'){
    if((mbase$FTHG[i] + mbase$AH[i] - mbase$FTAG[i]) > 0.25){
      mbase$Output[i] = "W"
    } else if((mbase$FTHG[i] + mbase$AH[i] - mbase$FTAG[i]) == -0.25){
      mbase$Output[i] = "LH"
    } else if((mbase$FTHG[i] + mbase$AH[i] - mbase$FTAG[i]) == 0){
      mbase$Output[i] = "VOID"
    } else if((mbase$FTHG[i] + mbase$AH[i] - mbase$FTAG[i]) == 0.25){
      mbase$Output[i] = "WH"
    } else if((mbase$FTHG[i] + mbase$AH[i] - mbase$FTAG[i]) < -0.25){
      mbase$Output[i] = "L"
    }
  } else if(substr(mbase$AHCode[i],1,1)=='A'){
    if((mbase$FTAG[i] + mbase$AH[i] - mbase$FTHG[i]) > 0.25){
      mbase$Output[i] = "W"
    } else if((mbase$FTAG[i] + mbase$AH[i] - mbase$FTHG[i]) == -0.25){
      mbase$Output[i] = "LH"
    } else if((mbase$FTAG[i] + mbase$AH[i] - mbase$FTHG[i]) == 0){
      mbase$Output[i] = "VOID"
    } else if((mbase$FTAG[i] + mbase$AH[i] - mbase$FTHG[i]) == 0.25){
      mbase$Output[i] = "WH"
    } else if((mbase$FTAG[i] + mbase$AH[i] - mbase$FTHG[i]) < -0.25){
      mbase$Output[i] = "L"
    }
 }
}; rm(i)

# Calculate the Net Profit and Lose (AH and OU odds without capital)
mbase$PL <- 0
for(i in seq(mbase$Output)){
  if(mbase$Output[i]=='W'){
    mbase$PL[i] <- mbase$COMOdds[i] * mbase$Staking[i]
  } else if(mbase$Output[i]=='WH'){
    mbase$PL[i] <- mbase$COMOdds[i] * mbase$Staking[i] * 0.5 
  } else if(mbase$Output[i]=='VOID'){
    mbase$PL[i] <-  0
  } else if(mbase$Output[i]=='LH'){
    mbase$PL[i] <- mbase$COMOdds[i] * mbase$Staking[i] * -0.5
  } else if(mbase$Output[i]=='L'){
    mbase$PL[i] <- mbase$COMOdds[i] * -mbase$Staking[i]
  } else {
    mbase$PL[i] <- NA
  }
}; rm(i)

# Calculate the Net Profit and Lose (AH and OU odds without capital and without overround/margin)
mbase$PL2 <- 0
for(i in seq(mbase$Output)){
  if(mbase$Output[i]=='W'){
    mbase$PL2[i] <- mbase$COMOdds[i] * mbase$Staking2[i]
  } else if(mbase$Output[i]=='WH'){
    mbase$PL2[i] <- mbase$COMOdds[i] * mbase$Staking2[i] * 0.5 
  } else if(mbase$Output[i]=='VOID'){
    mbase$PL2[i] <-  0
  } else if(mbase$Output[i]=='LH'){
    mbase$PL2[i] <- mbase$COMOdds[i] * mbase$Staking2[i] * -0.5
  } else if(mbase$Output[i]=='L'){
    mbase$PL2[i] <- mbase$COMOdds[i] * -mbase$Staking2[i]
  } else {
    mbase$PL2[i] <- NA
  }
}; rm(i)

mbase[1:100,-c(6:9,12:13)]
```

Summary of the betting
```{r}
Summary <- data.frame(
  Category = c('No of Matches','Total PL','No of Bets','No of Won Bets','No of Voided Bets','No of Lose Bets',
              'Staking','Won Bets Stakes','Voided Stakes','Lose Bets Stakes'),
  Bets_Wf_Overround = c(nrow(mbase), sum(mbase$PL), length(mbase[mbase$Staking>0,]$Staking), length(mbase[mbase$PL>0,]$PL),
                      length(mbase[mbase$PL==0 & mbase$Staking>0,]$PL), length(mbase[mbase$PL<0,]$PL),
                      sum(mbase[mbase$Staking>0,]$Staking), sum(mbase[mbase$PL>0,]$PL),
                      sum(mbase[mbase$PL==0 & mbase$Staking>0,]$Staking), sum(mbase[mbase$PL<0,]$PL)),
  Bets_No_Overround = c(nrow(mbase), sum(mbase$PL2), length(mbase[mbase$Staking2>0,]$Staking2), length(mbase[mbase$PL2>0,]$PL2),
                      length(mbase[mbase$PL2==0 & mbase$Staking2>0,]$PL2), length(mbase[mbase$PL2<0,]$PL2),
                      sum(mbase[mbase$Staking2>0,]$Staking2), sum(mbase[mbase$PL2>0,]$PL2),
                      sum(mbase[mbase$PL2==0 & mbase$Staking2>0,]$Staking2), sum(mbase[mbase$PL2<0,]$PL2)))

# Total Profit & Lose on different companies
COMPL <- data.frame(PL=sapply(split(mbase,mbase$COM), function(x) sum(x$PL)), PL2=sapply(split(mbase,mbase$COM), function(x) sum(x$PL2)))
Summary
COMPL
```
